---
title: "ZCTA to h3 Example"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

Suppose we want to find the estimated daily PM2.5 based on a patient's ZCTA.

1. Start with data containing ZCTA and start and end dates for each ZCTA.

```{r}
library(tidyverse)
d <- tibble::tribble(
  ~zcta, ~date, 
  "45229", "2018-06-30", 
  "45229", "2019-01-01", 
  "45220", "2019-06-30"
) %>% 
  mutate(start_date = as.Date(date),
         end_date = as.Date(date)) %>% 
  select(-date)

d
```

We can use the ZCTA to h3 crosswalk to covert our h3 gridded PM2.5 predictions to ZCTAs.

2. Download the ZCTA to h3 crosswalk file from s3.

```{r}
zcta_to_h3 <- s3::s3_get('s3://geomarker/h3/zcta_to_h3/zcta_2010_to_h3.rds') %>% 
  readRDS()
```

3. Join your data and the crosswalk file by `zcta`. 

```{r}
d <- left_join(d, zcta_to_h3, by = 'zcta')
d
```

4. Use `addPmData::add_pm` with `type = 'h3'` to add predicted PM for each h3 identifier. 

```{r}
# changes not merged yet, will be v0.0.4 
# remotes::install_github('geomarker-io/addPmData@h3-to-pm')
library(addPmData)
d <- add_pm(d, type = 'h3')
d
```

5. Multiply the predicted PM by the weights. 

```{r}
d <- d %>% 
  mutate(pm_pred_wt = weight*pm_pred)
```

6. Sum the product for each zcta-date combination to obtain weighted predicted PM. 

```{r}
d %>% 
  group_by(zcta, date) %>% 
  summarize(pm_pred_wt = sum(pm_pred_wt))
```

